Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-10 papers/ms.tex
update ms

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}.  %Based on the Q1-Q17 DR25 False
%Positive Probability table hosted at the NASA Exoplanet Archive, 
They
found a probability for any of the considered false positive scenarios
of 9$\times$10$^{-6}$.  Repeating the calculation with our own
stellar-variability correction and the new NIRC2 imaging constraints,
we find ${\rm FPP} = 6\times10^{-9}$, where the improvement is
presumably due to the new NIRC2 contrast curves.
Figure~\ref{fig:planets} shows the intuitive justification for the
result: the transit is flat and has a reasonably
high S/N ($\approx 47$), which is difficult to reproduce with
eclipsing binary models.

Intriguingly, Kepler-1643 also formally failed the
centroid shift test (see the \texttt{q1\_q17\_dr25\_koi} data release),
with the angular distance between the target star position and the
location of the transiting source being measured as $1\farcs0$
at 4.4-$\sigma$ confidence.  There seem to be two outlying quarters
(Q2 and Q6) driving the offset -- the centroid locations from the
other Kepler quarters are all consistent within $\lesssim 0\farcs5$.
Nonetheless, this is an instructive exercise in how variable stars can
complicate centroid-based vetting tests.  The centroid shifts measured
by these tests are determined from the in- and out-of-transit
flux-weighted centroids, but for our stars there is no static baseline
in either phase.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  The Q1-Q17 DR25 False Positive Probability table however
lists its probability of being an astrophysical false positive as
``1.0''. However, given that none of the other columns in this table
are populated, this is likely a database entry error ({\bf ask
Jessie}).  Performing the validation calculation using our new NIRC2
imaging constraints, we find ${\rm FPP} \approx 4\times10^{-3}$.
While not as convincing as Kepler-1643, this formally clears the
usual threshold for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit itself is
$\approx 32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve.  Visually, one can also inspect
each individual transit window in the light curve itself.  This
exercise shows a weak notch in each case; over the 198 observed
transits, the resulting signal seems sensible.

Why was KOI-7368 not previously validated?  One reason could be the
high stellar variability.  Another reason could be that it also
formally fails the centroid shift test, similar to Kepler-1643.  In
the case of KOI-7368, the reported offset is marginally less
significant ($0\farcs22$; 3.0-$\sigma$).  Again, inspection of the
data validation reports shows that this is caused by a few outlying
quarters: in this case Q4, Q5, Q8, and Q12.  The fact that the
remaining quarters show a more consistent scatter suggests that these
outliers are again caused by stellar variability local to the
transits, rather than by an astrophysical offset.  Our imaging also
shows that there are no neighboring sources that could cause an
offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is listed on the NASA Exoplanet Archive as a ``CANDIDATE''
planet.  The Q1-Q17 DR25 False Positive Probability table lists its
probability of being an astrophysical false positive as
$1.4\times10^{-4}$, with the most likely false positive scenario being
a blended eclipsing binary.  Repeating the calculation with our new
detrending and contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  While the transit has the lowest S/N of any of the
objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).

The disposition of KOI-7913.01 has previously been debated:
in \texttt{q1\_q17\_dr25\_koi} the source was flagged as a ``FALSE POSITIVE'',
with the comment ``CENT\_KIC\_POS---HALO\_GHOST''.  This comment and
disposition seem to have been removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed it a
``CANDIDATE'', without any flag given.  As described by
\citet{thompson_planetary_2018}, the ``CENT\_KIC\_POS'' flag is an
indication that the measured source centroid is offset from its
expected location in the Kepler Input Catalog.  The final Data
Validation Reports, generated 2016 Jan 30, do not seem to show this.
Moreover, the statistical significance of any centroid offset seems to
be lower than for KOI-7368 and Kepler-1643 (which, as we have argued,
both show centroid offsets that seem to be explained by the stellar
variability).

What of the ``HALO\_GHOST'' flag?  This test measures the transit
strength for the pixels inside the aperture, and compares it to that
measured in the ring of pixels around said aperture (the ``halo'').
Generally one expects the transit signal to be strongest in the
central aperture, rather than the halo.  Two types of false positive
scenarios can change this and trigger the flag: the first is when
optical ghosts from bright eclipsing binaries reflect off the CCD, and
contaminate the target star.  The second is when the PRF of nearby
stars directly overlaps with the PRF of the target star (see
\citealt{thompson_planetary_2018}, Section A.5.2).

The most obvious explanation for KOI-7913 is the latter case, since
KOI-7913 B is $\approx0.9$ Kepler pixels away from Kepler-7913 A.  Due
to the on-sky orientation of KOI-7913 A and KOI-7913 B, the default
``optimal aperture'' selected in Q3, Q7, Q11, and Q15 in fact included
both stars, while for the remaining quarters KOI-7913 B was
(correctly) excluded from the optimal aperture (see pages 35 through
71 of the Data Validation Report.)

As a test, we opted to re-extract the light curves from the target
pixel files for these particular cases.
{\bf Comparing the pixels on-target, and found}
%FIXME FIXME TODO TODO
{\bf We found...}

@@

>>>>

\paragraph{Kepler-1643}
  %Based on the Q1-Q17 DR25 False Positive Probability table hosted at
%the NASA Exoplanet Archive, 
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$), which is
difficult to reproduce with eclipsing binary models.

Intriguingly, Kepler-1643 formally failed one of the centroid shift
tests (see the \texttt{q1\_q17\_dr25\_koi} data release): the angular
distance between the target star's catalog position and the position
of the transiting source was measured as $1\farcs0$ at 4.4-$\sigma$.
The reports show however that two outlying quarters (2 and 6) 
drive the offset -- the centroid locations from the other Kepler
quarters are consistent at $\lesssim 0\farcs4$.  Nonetheless, this
is an instructive exercise in how stellar variability complicates
centroid-based vetting tests.  The centroid shifts measured by these
tests are determined from the in- and out-of-transit flux-weighted
centroids.  For stars with significant spot-induced
variability there is no static baseline in either the in- or
out-of-transit phases.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.
%The Q1-Q17 DR25 False Positive Probability table however lists its
%probability of being an astrophysical false positive as ``1.0''. Given
%that none of the other columns in the table are populated, this seems
%likely to be a database entry error ({\bf ask Jessie}). 
Our fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the validation
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements
for transiting sources thought to share positions with their
target stars \citep{morton_false_2016,2017ksci.rept...16B}. 
%A visual inspection of
%each individual transit also shows a weak notch at the predicted
%transit times; over the 198 observed transits, the resulting signal
%seems sensible.

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
statistically significant ($0\farcs2$; 3.0-$\sigma$).  Again,
the data validation reports show that the shift is caused by a few
outlying quarters (4, 5, 8, and 12).  The fact that the remaining data
show a consistent scatter between centroid locations suggests that
these outliers are also caused by the stellar variability.  Independently, our
imaging shows that there are no neighboring sources that could
cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016} analysis
was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01 to
KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from Kepler-7913 A (see
Appendix~\ref{app:koi7913}).  Our pixel-level analysis of the target
pixel files did not show any evidence to support the idea that
KOI-7913~B could host the transiting planet.  Our NIRC2 imaging
similarly ruled out the possibility of any other plausible host star
for the planet other than KOI-7913~A.

@@

\section{Disposition History of KOI-7913}
\label{app:koi7913}

The disposition of KOI-7913.01 has been debated: in
\texttt{q1\_q17\_dr25\_koi} the source was flagged as a false
positive, with the comment ``cent\_kic\_pos---halo\_ghost''.  This
comment and disposition were removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed the
planet a ``candidate''.  In this note, we discuss the interpretation
of these flags (which do not apply to the system, according to the
latest analysis).  We also discuss how the relative locations of
KOI-7913~A and KOI-7913~B affect the interpretation of the Kepler
data.

As described by \citet{thompson_planetary_2018}, the
``cent\_kic\_pos'' flag is an indication that the measured source
centroid is offset from its expected location in the Kepler Input
Catalog.  The final Kepler data validation reports, generated 2016 Jan
30, do not show this to be the case for KOI-7913.  Moreover, the
statistical significance of any centroid offset is lower than for
KOI-7368 and Kepler-1643 (which both show centroid offsets that are
likely explained by the stellar variability).

What of the ``halo\_ghost'' flag?  This test measures the transit
strength for the pixels inside the aperture, and compares it to that
measured in the ring of pixels around said aperture (the ``halo'').
Generally one expects the transit signal to be strongest in the
central aperture, rather than the halo.  Two types of false positive
scenarios can change this and trigger the flag: the first is when
optical ghosts from bright eclipsing binaries reflect off the CCD, and
contaminate the target star.  The second is when the PRF of nearby
stars directly overlaps with the PRF of the target star (see
\citealt{thompson_planetary_2018}, Section A.5.2).
The most obvious explanation for KOI-7913 is the latter case, given
that KOI-7913 B is $\approx0.9$ Kepler pixels away from Kepler-7913 A
and so it usually part of the ``halo''.  Due to the on-sky orientation
of KOI-7913 A and KOI-7913 B, the default ``optimal aperture''
selected in quarters 3, 7, 11, and 15 in fact included both stars,
while for the remaining quarters KOI-7913 B was excluded from the
optimal aperture but was included as part of the halo (see pages 35
through 71 of the data validation reports.)

Given the orientation of the stars and the $\approx$1.5 pixel FWHM of
the Kepler pixel response function, some blending between the two
stars is present.  The pointing geometries from quarters 3, 7, 11, and
15 however did not noticeably affect the observed transit depths,
which is an indication that the crowding metric applied in the data
products accurately correct the mean flux level
\citep{2017ksci.rept....6M}.  Analysis of the target-pixel data that
was acquired separately for KOI-7913~B also reveals a clearly
different stellar rotation period, and no hint of the transit signal.
